Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-12 Codes/PrepareResults.rmd
Incorporate Dr.Bullock's comments and add Mendeley data citation (additional)

  # theme(    
  #   strip.text.x = element_text(size = 12, face = "bold"),
  #   legend.title = element_text(size = 12, face = "bold"),
  #   legend.text = element_text(size = 12, face = "bold"),
  #   legend.position = "bottom",
  #   text  = element_text(family = "Times New Roman")
  # )

@@

```{r setup, warning=FALSE, message=FALSE, cache= FALSE}
# field <- readRDS("Shared/Data/for_Simulations/field_padding.rds") %>%
#     filter(padding==1)%>%
#     dplyr::select(unique_cell_id)

# === plot-level field data set  === #
field_plot_sf <-
  here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
  readRDS()

@@

plot <-
  ggplot() +
  geom_sf(data = field_plot_sf) +
  geom_sf(data = ex_plot, fill = "green", size = 1) +
  coord_sf(expand = FALSE) +
  ggtitle("12 \u00D7 12 subplots") +
  # ggtitle(TeX("$12 \\times 32$ plots")) +
  theme_figure

@@

#-- (2) create a map of subplots in a plot --##
subplots_inPlot <- 
  ggplot() +
  geom_sf(data = ex_plot, fill = "green") +
  geom_sf(data = ex_subplots, fill = NA, size = 1) +
  geom_sf(data = ex_subplots[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  theme_void() +
  # ggtitle(TeX("$4 \\times 1$ subplots")) +
  ggtitle("4 \u00D7 1 subplots") +
  theme_figure

@@

#-- (3) create a map of cells in a subplot --#
cells_inSubplot <-
  ggplot() +
  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
  geom_sf(data = ex_cells, fill = NA) +
  geom_sf(data = ex_cells[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  theme_void() +
  # ggtitle(TeX("$6 \\times 6$ cells")) +
  ggtitle("6 \u00D7 6 cells") +
  theme_figure

@@

#-- (4)put them on the same map --#
field_structure <-
  ggplot() +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)+
  # /*----------------------------------*/
  #' ##  base maps
  # /*----------------------------------*/
  # --- plot level --- #
  annotation_custom(grob_plot,
    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1) +
  # --- subplot level --- #
  annotation_custom(grob_subplots_inPlot,
    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7) + 
  # --- cell level --- #
  annotation_custom(grob_cells_inSubplot,
    xmin = 0.8, xmax = 0.8+0.2, ymin = 0.382, ymax = 0.382 +0.2) +
  #/*----------------------------------*/
  #' ## Add braces
  #/*----------------------------------*/
  # --- between plot and subplot --- #
  geom_brace(aes(c(0.43,0.43+0.1), c(0.353, 0.661)), color ="red", rotate = 270, inherit.data=F) +
  # --- between subplot and cell --- #
  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.381, 0.549)), color ="red", rotate = 270, inherit.data=F) +
  #/*----------------------------------*/
  #' ## add annotations
  #/*----------------------------------*/
  # --- annotation for plot --- #
  geom_segment(aes(x = 0.42, xend = 0.383, y = 0.60, yend = 0.52),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.015, label = "plot", family="Times New Roman") +
  # --- annotation for subplot --- #
  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family="Times New Roman") +
  # --- annotation for cell --- #
  geom_segment(aes(x = 0.89, xend = 0.86, y = 0.349, yend = 0.394),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.89 + 0.015, y = 0.349 - 0.01, label = "cell", , family="Times New Roman") +
  theme_void()
```

@@

# Preparation for exmaple field maps (one-time run)

```{r}
# source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")

# pCorn <- price_table[2, pCorn]
# pN <- price_table[2, pN]

# /*=================================================*/
#' # Field Data Sets
# /*=================================================*/

#/*----------------------------------*/
#' ## (1) cell-level data set 
#/*----------------------------------*/
# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
# field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))

# coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))

# x=1
# coef_data_m <- coef_data[sim == x, ]
# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]

# sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
#   .$reg_raw_data

# field_cell_sf <- 
#   left_join(dplyr::select(field, unique_cell_id), sample_dt_cell, by="unique_cell_id")%>%
#     na.omit() %>%
#     mutate(plot_id = ceiling(subplot_id/4)) %>%
#     filter(padding==1)

# saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))

#/*----------------------------------*/
#' ## (2) subplot-level field without padding area 
#/*----------------------------------*/

# field_subplot_sf <- 
#   field_cell_sf %>%
#   group_by(subplot_id, strip_id) %>%
#   summarise(
#     sim = mean(sim),
#       yield = mean(yield),
#       opt_N = mean(opt_N),
#       rate = mean(rate),
#       aa_n = mean(aa_n), 
#       alpha = mean(alpha),
#       beta = mean(beta),
#       ymax = mean(ymax),
#       alpha1 = mean(alpha1),
#       alpha2 = mean(alpha2),
#       beta1 = mean(beta1),
#       beta2 = mean(beta2),
#       ymax1 = mean(ymax1),
#       ymax2 = mean(ymax2),
#       theta_1 = mean(theta_1),
#       theta_2 = mean(theta_2)
#   ) %>%
#   mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
#   dplyr::select(!c(strip_id, subplot_id))

# saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))

#/*----------------------------------*/
#' ## (3) plot-level dataset without padding area  
#/*----------------------------------*/
# field_plot_sf <- field_cell_sf%>%
#     group_by(plot_id, strip_id, rate)%>%
#     summarise()

# saveRDS(field_plot_sf, here("Shared/Results/for_writing/sample_field_plot_sf.rds"))
```

>>>>

@@

```{r setup, warning=FALSE, message=FALSE, cache= FALSE}
# === plot-level field data set  === #
field_plot_sf <-
  here("Shared/Results/for_writing/sample_field_plot_sf.rds") %>%
  readRDS()

@@

plot <-
  ggplot() +
  geom_sf(data = field_plot_sf) +
  geom_sf(data = ex_plot, fill = "green", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle("12 \u00D7 12 subplots") +
  theme_figure

@@

#-- (2) create a map of subplots in a plot --##
subplots_inPlot <- 
  ggplot() +
  geom_sf(data = ex_plot, fill = "green") +
  geom_sf(data = ex_subplots, fill = NA, size = 1) +
  geom_sf(data = ex_subplots[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle("4 \u00D7 1 subplots") +
  theme_figure

@@

#-- (3) create a map of cells in a subplot --#
cells_inSubplot <-
  ggplot() +
  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
  geom_sf(data = ex_cells, fill = NA) +
  geom_sf(data = ex_cells[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle("6 \u00D7 6 cells") +
  theme_figure

@@

#-- (4)put them on the same map --#
field_structure <-
  ggplot() +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)+
  # /*----------------------------------*/
  #' ##  base maps
  # /*----------------------------------*/
  # --- plot level --- #
  annotation_custom(grob_plot,
    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1) +
  # --- subplot level --- #
  annotation_custom(grob_subplots_inPlot,
    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7) + 
  # --- cell level --- #
  annotation_custom(grob_cells_inSubplot,
    xmin = 0.8, xmax = 0.8+0.2, ymin = 0.382, ymax = 0.382 +0.2) +
  #/*----------------------------------*/
  #' ## Add braces
  #/*----------------------------------*/
  # --- between plot and subplot --- #
  geom_brace(aes(c(0.43,0.43+0.1), c(0.372-0.004, 0.645+0.013)), color ="red", rotate = 270, inherit.data=F) +
  # --- between subplot and cell --- #
  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.401-0.002, 0.529 +0.011)), color ="red", rotate = 270, inherit.data=F) +
  #/*----------------------------------*/
  #' ## add annotations
  #/*----------------------------------*/
  # --- annotation for plot --- #
  geom_segment(aes(x = 0.42, xend = 0.383, y = 0.60, yend = 0.52),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.02, label = "plot", family="Times New Roman") +
  # --- annotation for subplot --- #
  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family="Times New Roman") +
  # --- annotation for cell --- #
  geom_segment(aes(x = 0.9, xend = 0.87, y = 0.365, yend = 0.41),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.9 + 0.02, y = 0.365 - 0.005, label = "cell", , family="Times New Roman") +
  theme_void()
```

@@

### 2022-02-12 Writing/CEA_2nd_round/replies_rev_1.rmd
Incorporate Dr.Bullock's comments and add Mendeley data citation (additional)

---
title: "Reply to Reviewer #1"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: word_template_format.docx
---

Thank you so much for your comments. By addressing them, we believe the manuscript is improved significantly. You can find our replies to your comments. Your comments are in bold, and out replies are in a regular font.

@@

<span style="color:blue">  
Yes, we agree with your point, and we have decided to simply drop it from our highlights.
</span>

@@

We do see a redundancy of expalining how CF can be used to identify site-specific input recommendations. It was explained twice in 2.2 and 3.2.2, while 2.2 is intended for a more general case than 3.2.2 that is specific to our simulations. Therefore, we decided to take out 2.2. We also renamed 2.1 to "Estimating EOIR and Treatment Effects."

We have moved an example of causal tree (previously in seciton 2.3), but decide to keep the explanation of how CF works. The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations. To this core objective, ML simulation is our core method. For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give too much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal. However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well. Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works. Insted, we believe that it is better to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted. Therefore, we kept 2.3 and 2.4 (in the previous round) in the current manuscript.
</span>

@@

First, we consolidated 3.1.2 and 3.1.3 in the previous round into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we dropped detailed explanation of the conceptual framework behind the yield response functions based on cell-leve characteristics, $c_i$, and moved it to the supplemnentary appendix (Appendix B). We also removed our detailed description of how parameters and error term were generated and moved it to Appendix C along with relevant tables and figures (spefically table x and figures x, y, z) <span style = "color: blue;"> Shun put table and figure numbers here </span>.

Second, we consolidated 3.1.4 and 3.1.5 in the previous round into a single subsubsection called "Trial Design and Yield Data Generation for Modeling." In doing so, we cut some texts and combined figure x and y in the previous round into a single figure (figure x in the current manuscript).

Third, we removed detailed description of how some parameters are splitted into two parts and moved it to the Appendix.

In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated. It is much like any emprical studies using real experiment data provides lots of details about the experiemnts. We take reproducibility seriously and we believe that the details we peovided in our current manuscript is appropriate and it is hard for us to further slim down the section. Moreover, we believe we no longer have any redundancy in this section. 
</span>

@@

<span style="color:blue">  
It is degree. The unit is now provided in the description of the figure in Appendix A. Please not that this example is just for illustrating how CF works.
</span>

@@

<span style="color:blue">  
Explanations for those numbers are added as a footnote to the figure. The figure is now in the appendix and called Figure A.1. 
</span>

@@

<span style="color:blue">  
All the formulas are now numbered. <span style = "color: blue;"> Shun, make sure this happens right before you submit. </span>
</span>

@@

<span style="color:blue">  
We aplogogize that we are not clear on this respect.

Trainign dataset and test dataset are completely separate. For a given simulation round, the training dataset in another round of simulation acts as a "test" dataset. These datasets are created independently from one another and are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$. Therefor, in MC simulations, the dataset in a given simulation serves as a train dataset, and served as a test data for another simulation round. The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters within a given simulation round.

We added the following paragraph to section <span style = "color: blue;"> Shun section number here </span> to make this point clear.

"For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset. For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset. This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$). Furtehr, each of the "train" datasets are generated independet of one another. Thefore, for a particular simulation round, the dataset in any of the other simualtion rounds can serve as a valid test dataset. This practice avoid creating another set of 1000 simulations fields unnecessarily."
</span>

@@

<span style="color:blue">  
The simulation codes and the data were also shared on Mendeley Data (<span style = "color: blue;"> Shun, provide the link here </span>) according to the Editor's suggestion for the ease of access. The link is also provided <span style = "color: blue;"> Shun, be speficic about where it is </span>.

<span style = "color: blue;"> Shun, make sure you cite the code and data. </span>

We realized that the github repository was private and that was why you were not able to access it. We made a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).
</span>

@@

<span style="color:blue">  
All the lenth units were converted to meter (m)
</span>

@@

<span style="color:blue">  
The number of rows and columns of plots, subplots, and cells schematics are now indicated Figure 2.
</span>

@@

<span style="color:blue">  
We realized that section 3.1 also had a uninformative title. Therefore, we changed it to "Training Models and Estimating Site-specific EONRs". Further, the title of sections 3.2.1 and 3.2.2 were changed to "Estimation of site-specific EONRs by RF, BRF, and CNN" and "Estimation of site-specific EONRs by CF", respectively. 
</span>

@@

<span style="color:blue">  
The title of 4.1 was changed to "Comparison of EONR estimation accuracy" to reflect its contents. The title of section 4.2 was changed to "The relationship between yield and EONR prediction performances". They acurrately reflect what they describe.
</span>

@@

As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1). Therefore, we thought that visualizing the CNN results are not insightful. However, we have decided to include CNN results to Figures 8, 9, and 10 in the previous version. The figures are now Figures 3, 4, and 5.

@@

<span style="color:blue">  
We added a new section called "Limitations and Future Studies" before the Conclustion section. One of the important assumptions that needs to be satisfied for CF to provides consistent estimation of treatment effects is that the treatment (N rates here) is uncorrelated with unobservable characteristics. Other assumtions are relatively minor. Note that, this is not just for CF, but also for RF, BRF, and CNN. Whenever the variable of interest (N rates here), their estiamtion of its impact on the dependent variable is biased in general. Fortunatley, in OFPE settings, we can randomize or patternize the input rates in a way that the input rates are uncorrelated to the unobserved variables. Therefore, the violation of this assumption is not as much of a concener as in a setting where observational data is used. We discuss these in the "Trial Design and Yield Data Generation for Modeling" section. 
</span>

@@

<span style="color:blue">  
We moved the descriptions of the limitations (uncertainty) of the study to a separate section as mentioned earlier in our reply to your comment 14.
</span>

>>>>

---
title: "Reply to Reviewer #1"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: ../word_template_format.docx
---

Thank you so much for your comments. By addressing them, we believe the manuscript is improved significantly. Below you will find your comments in bold and our replies in a regular font.

@@

<span style="color:blue">  
We agree with your point, and we have dropped the discussion of the advantages of the CF model from our highlights.
</span>

@@

We do see a redundancy in our explanation of how CF can be used to identify site-specific input recommendations. It was explained twice, once each in subsections 2.2 and 3.2.2. We have deletedthe explanation in 2.2 and also changed the heading in 2.1 to "Estimating EOIR and Treatment Effects."

We have moved an example of a causal tree (previously in seciton 2.3), but have kept the explanation of how CF works. The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations.

ML simulation is the core method we use to pursue this core objective. For this reason the Materials and Methods section features no explanation of how CF works. We also provide little explanation of RF, BRF, and CNN methods, which are well-established and familiar to many readers of this journal. However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present in detail how it works and the conditions necessary for it to work well. We believe that if we placed such a description of how CF works inside the Materials and Method section, it will unnecessarily distract the reader by breaking the flow of the explanation of the MC simulation procedures. We feel that the narrative will flow better if it first informs readers about the potential advantages of CF over existing prediction-oriented ML methods before moving into a description of the MC simulations in the Materials and Method section. Therefore, we have kept in the current manuscript the discussion located in subsection 2.3 and 2.4 of the original manuscript.
</span>

@@

First, in the new manuscript we consolidated the original manuscript's 3.1.2 and 3.1.3 into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we moved to the supplementary appendix (Appendix B) the detailed explanation of the conceptual framework behind the yield response functions based on cell-level characteristics, $c_i$. In addition, we moved to Appendix C our detailed discussion of parameters and error term generation, which included a number of tables and figures. <span style = "color: blue;"> Shun put table and figure numbers here </span>.

Second, we consolidated subsection 3.1.4 and 3.1.5 of the original manuscript into a single subsubsection called "Trial Design and Yield Data Generation for Modeling." In doing so, we removed some text and combined the original manuscript's figures x and y in the single figure z in the current manuscript.

Third, we moved to an appendix the previous manuscript’s detailed description of parameter splitting.

We believe that the detailed presentation of data generation is crucial in our reporting of MC procedures, as it would be in the report of any empirical study using real experiment data provides. In both cases, results are highly dependent procedures. We believe further slimming of the description would hinder anyone attempting to reproduce our results. That said, we have worked hard to remove redundancies in this section of the manuscript. 
</span>

@@

<span style="color:blue">  
It is degree. The unit is now provided in the description of the figure in Appendix A. Please note that the purpose of the example is simply to illustrate how CF works.
</span>

@@

<span style="color:blue">  
Explanations for those numbers are added as a footnote to the figure. The figure is now in an appendix and called Figure A.1. 
</span>

@@

<span style="color:blue">  
All the formulas are now numbered.
</span>

@@

<span style="color:blue">  
We apologize for not making this cleaner in the original manuscript. The training data set and test data set were completely separate in our analysis. For a given simulation round, the training data set from another round acted as a "test" dataset. These data sets were created independently and with different underlying field parameters $\alpha$, $\beta$, and $ymax$. Training data sets, however, were split into several parts for cross-validation in determining a round's optimal values of its hyperparameters. In addition, we added the following paragraph section 3.3.3 to make this point clear.

"For evaluation of yield and EONR predictions, a data set from a different simulation round was used as the test data set. For example, for simulation number 1, the training data set from simulation number 2 was used as the test data set. This process works because the training data sets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$). Further, all training data sets were generated independently, so for any particular simulation round, the data set from any other round could serve as a valid test data set. This practice made the creation of one thousand additional simulations fields unnecessary."
</span>

@@

<span style="color:blue">  
We have followed the Editor's suggestion by sharing the simulation codes and the data on Mendeley Data (https://data.mendeley.com/datasets/y7cdhzww6w/draft?a=2e33b309-ca5c-49bc-95ce-9b3920d5544a) to increase the accessibility. The name of the data set is "Codes and Data Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation", and two folders are included in this data set: "Codes" and  "Data". The "Code" folder contains all the simulation codes, and the "Data" folder contains a boundary polygon data of a field which is necessary to create field data for this study. Please read README.md for the steps to reproduce. In addition, we created a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA))
</span>

@@

<span style="color:blue">  
Done
</span>

@@

<span style="color:blue">  
Done. Please see Figure 2. 
</span>

@@

<span style="color:blue">  
We changed the title of 3.2 to "Training Models and Estimating Site-specific EONRs", and the title of 3.2.1 and 3.2.2 to "Training and Estimation of Site-specific EONRs by RF, BRF, and CNN" and "Training and Estimation of Site-specific EONRs by CF".
</span>

@@

<span style="color:blue">  
To better reflect the contents of 4.1, we changed its title to "Comparison of EONR Estimation Accuracy." We changed the title of 4.2 to "The Relationship between Yield and EONR Prediction Performances." Both new headings provide more accurate descriptions of their subsection's contents.
</span>

@@

As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (Table 1). Therefore, we thought that visualizing the CNN results would not provide much insight. However, we have decided to include CNN results in Figures 8, 9, and 10 of the previous manuscript. which are Figures 3, 4, and 5 of the revised manuiscript.

@@

<span style="color:blue">  
We have added a section called “Limitations and Future Studies” before the Conclusion section of the revised manuscript. One of the important conditions for CF to provide consistent estimation of treatment effects is that the treatment (N rates here) is uncorrelated with unobservable characteristics. Other assumptions are relatively minor. Note that, this is not just for CF, but also for RF, BRF, and CNN. Whenever the variable of interest (N rates here), their estimation of its impact on the dependent variable is biased in general. Fortunately, in OFPE settings we can randomize or geographically pattern input rates to make them uncorrelated with unobserved variables. Therefore, the violation of this assumption is not as much of a concern as in a setting where observational data is used. We discuss these in the “Trial Design and Yield Data Generation for Modeling” section. 
</span>

@@

<span style="color:blue">  
As mentioned earlier in our reply to your comment 14, in the revised manuscript we have moved the descriptions of the limitations (uncertainty) of the study to a separate section. 
</span>

### 2022-02-12 Writing/appendix.rmd
math equation fixes
Update figures and tables
1. position of R2 labels are changed and the figure height increased to 7.5 2. minor changes in manuscript
Incorporate Dr.Bullock's comments and add Mendeley data citation (additional)

NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha). The number and the percentage of observations belonging to the node are shown below that.

In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example. The first data split criterion is whether the $\textit{ecs}$ value is greater or less than $25$. The observations with $\textit{ecs}$ greater than or equal to $25$ move to the left node, while those with $\textit{ecs}$ less than $25$ move to the right. For each of the subsamples, the treatment effect is identified as the difference in the mean yields of the treated and control groups within the subsample. The treatment effect for the low-$\textit{ecs}$ observations was $619$ kg/ha, and for the high-$\textit{ecs}$ observations was $982$ kg/ha. This means that for the impact of the increase in seed rate the treatment effect is heterogeneous over space, having a larger positive impact on yield in high-$\textit{ecs}$ areas. Trees are further developed to have more groups of subsamples to allow for more flexible representations of the heterogeneous treatment effects. The estimated heterogeneous treatments effects can then be used to identify site-specific EOIRs. It is noteworth that at no point CF estimates yield "level".

@@

\begin{alinged}
f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon. 
\end{alinged}

@@

\begin{equation}
f(N_{i}, \mathbf{c}_{i}) = ymax(\mathbf{c}_{i})(1-exp(\alpha(\mathbf{c}_{i}) + \beta(\mathbf{c}_{i}) N_{i})) + \varepsilon_{i}. 
\end{equation}

@@

Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project. (Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) The range and nugget of all parameters were assumed to be $400$ m and 0. The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$. See Figure \@ref(fig:fig-parameters) for an example of the generated parameters.

@@

field_alpha + field_beta + field_ymax + field_m_error + vis_optN_cell + plot_layout(ncol = 2)
```

@@

For scenarios "aabbyy" and "aabbyytt", each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner. Speficiallu, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r^{\alpha}_{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r^{\beta}_{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r^{ymax}_{i,j} \in (0,1)$ to the ${ymax}_{i,j}$ variable. Each of the weight variables are generated using unconditional Gaussian geostatistical simulation just like the base parameters. (There was no spatial correlation between the $r^{\alpha}_{i,j}$ and $r^{\beta}_{i,j}$ data, between $r^{\alpha}_{i,j}$ and $r^{ymax}_{i,j}$ data, or between $r^{\beta}_{i,j}$ and $r^{ymax}_{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha_{i,j}$, $\beta_{i,j}$ and $ymax_{i,j}$. These were 
$\alpha_{1}_{i,j} = r^{\alpha}_{i,j} \alpha_{i,j}$, $\alpha_{2}_{i,j} = (1- r^{\alpha}_{i,j}) \alpha_{i,j}$,
$\beta_{1}_{i,j} = r^{\beta}_{i,j} \beta_{i,j}$, $\beta_{2}_{i,j} = (1- r^{\beta}_{i,j}) \beta_{i,j}$,
$ymax_{1}_{i,j} = r^{ymax}_{i,j} ymax_{i,j}$, and $ymax_{2}_{i,j} = (1- r^{ymax}_{i,j}) ymax_{i,j}$. The codes used to implement the abovementioned parameter splitting is available at https://github.com/tmieno2/ML_VRA.git.

<span style = "color: blue;"> Shun, provide the link to Mandeley data and cite it </span>

>>>>

`r ftext('NOTE: The first number in each node indicates the predicted treatment effects (in kg/ha). The number and the percentage of observations belonging to the node are shown below that.', fp_text(font.size = 9, font.family = "Times New Roman"))`

In the first node, all the samples ($1024$ observations) belong to the node, and the causal effect of the treatment was calculated as the difference in the mean yield of the treated and control groups, which turned out to be $593$ kg/ha in this example. The first data split criterion is whether the $\textit{ecs}$ value is greater or less than $25$. The observations with $\textit{ecs}$ greater than or equal to $25$ move to the left node, while those with $\textit{ecs}$ less than $25$ move to the right. For each of the subsamples, the treatment effect is identified as the difference in the mean yields of the treated and control groups within the subsample. The treatment effect for the low-$\textit{ecs}$ observations was $619$ kg/ha, and for the high-$\textit{ecs}$ observations was $982$ kg/ha. This means that for the impact of the increase in seed rate the treatment effect is heterogeneous over space, having a larger positive impact on yield in high-$\textit{ecs}$ areas. Trees are further developed to have more groups of subsamples to allow for more flexible representations of the heterogeneous treatment effects. The estimated heterogeneous treatments effects can then be used to identify site-specific EOIRs. It is noteworth that at no point CF estimates yield "level."

@@

\begin{alinged}
f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) \cdot N)) + \varepsilon. 
\end{alinged}

@@

\begin{equation}
f(N_{i}, \mathbf{c}_{i}) = ymax(\mathbf{c}_{i})(1-exp(\alpha(\mathbf{c}_{i}) + \beta(\mathbf{c}_{i})\cdot N_{i})) + \varepsilon_{i}. 
\end{equation}

@@

Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project. (Codes used to generate parameter values are available at @Kakimoto2022codes.) The range and nugget of all parameters were assumed to be $400$ m and 0. The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$. See Figure \@ref(fig:fig-parameters) for an example of the generated parameters.

@@

field_alpha + field_beta + field_ymax + field_m_error + field_optN + plot_layout(ncol = 2)
```

@@

For scenarios "aabbyy" and "aabbyytt," each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner. Specifically, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r^{\alpha}_{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r^{\beta}_{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r^{ymax}_{i,j} \in (0,1)$ to the ${ymax}_{i,j}$ variable. Each of the weight variables are generated using unconditional Gaussian geostatistical simulation just like the base parameters. (There was no spatial correlation between the $r^{\alpha}_{i,j}$ and $r^{\beta}_{i,j}$ data, between $r^{\alpha}_{i,j}$ and $r^{ymax}_{i,j}$ data, or between $r^{\beta}_{i,j}$ and $r^{ymax}_{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha_{i,j}$, $\beta_{i,j}$ and $ymax_{i,j}$. These were 
$\alpha^{1}_{i,j} = r^{\alpha}_{i,j} \cdot \alpha_{i,j}$, $\alpha^{2}_{i,j} = (1- r^{\alpha}_{i,j}) \cdot \alpha_{i,j}$,
$\beta^{1}_{i,j} = r^{\beta}_{i,j} \cdot\beta_{i,j}$, $\beta^{2}_{i,j} = (1- r^{\beta}_{i,j}) \cdot\beta_{i,j}$,
$ymax^{1}_{i,j} = r^{ymax}_{i,j} \cdot ymax_{i,j}$, and $ymax^{2}_{i,j} = (1- r^{ymax}_{i,j}) \cdot ymax_{i,j}$. The codes used to implement the abovementioned parameter splitting is available at @Kakimoto2022codes.
